### 2021-09-11 draft.tex
Deploy to GitHub Pages

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}\quad %
Peregrin\,Took%
%
\,\textsuperscript{3,4}\quad %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Inn of the Prancing
Pony\quad \textsuperscript{4}\,Fellowship of the
Ring\quad \textsuperscript{5}\,Green Dragon Inn

\textsuperscript{‡}\,These authors contributed equally to the work\\

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

This template uses \texttt{pandoc} (and a few additional python glue
scripts) to facilitate the production of scientific articles using a
standard markdown file. The objective is to ensure that standard
markdown (with the important exception of the \texttt{pandoc-crossref}
citation markup) will be rendered into an interactive website (which
allows collaborative annotations with the \texttt{hypothes.is}
platform), a ``draft'' style PDF (double-spaced, numbered lines, figures
at the end), and a ``preprint'' style PDF (with slightly more
reader-friendly pagination).

The core bit of configuration is the \texttt{metadata.json} file, which
handles information about authorship, affiliations, the abstract,
keywords, etc. All documents will be deployed to \texttt{gh-pages}
\emph{only} on push events from the \texttt{main} branch. All of the
artifacts will be built when doing pull requests, so you can check that
merging a branch is \emph{not} going to cause the compilation of the
documents to fail; indeed, you can download the artifacts produced
during the run, to check the PDF and html files. The website is only
updated from the \texttt{main} branch.

The workflow is \emph{very} GitHub based, and so the manuscript file
\emph{is} the \texttt{README.md} - this is not going to be a huge issue
as 90\% of the markdown is standard, with the exception of the citations
and mathematics, so this will render (mostly) like a normal README file.

\hypertarget{deploying-the-template}{%
\section{Deploying the template}\label{deploying-the-template}}

\begin{itemize}
\tightlist
\item
  Click on the ``Use this template'' button
\item
  Edit this README!
\item
  Add an \texttt{ACCESS\_TOKEN} secret to your repository
\item
  Trigger a build by pushing a commit - the builds are only active on
  the \texttt{main} (\textbf{not} \texttt{master}) branch, and on pull
  requests
\item
  Go to \texttt{http://you.github.io/repo-name/} to view the html
  version and the PDFs
\item
  Add your references to the \texttt{references.bib} file
\item
  Edit the \texttt{metadata.json} file to add the title, abstract,
  authors
\item
  Edit the \texttt{manuscript.md} file to make changes to your text
\end{itemize}

\hypertarget{the-metadata-file}{%
\section{The metadata file}\label{the-metadata-file}}

\hypertarget{general-information}{%
\subsection{General information}\label{general-information}}

The first three fields are the title, language, and license. It's
probably advisable not to change these, and there are chances that the
logo on the PDF will not capture the values made here (this will have to
be, maybe, fixed at some point).

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{}
    \DataTypeTok{"title"}\FunctionTok{:} \StringTok{"Preprint template"}\FunctionTok{,}
    \DataTypeTok{"license"}\FunctionTok{:} \StringTok{"CC{-}BY"}\FunctionTok{,}
    \DataTypeTok{"language"}\FunctionTok{:} \StringTok{"en"}
\FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{authorship}{%
\subsection{Authorship}\label{authorship}}

Authors are listed as objects in the \texttt{authors} block. Each author
is specified as follows:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{}
      \DataTypeTok{"familyname"}\FunctionTok{:} \StringTok{"Bob"}\FunctionTok{,}
      \DataTypeTok{"givennames"}\FunctionTok{:} \StringTok{"Alice"}\FunctionTok{,}
      \DataTypeTok{"email"}\FunctionTok{:} \StringTok{"alice.bob@u.edu"}\FunctionTok{,}
      \DataTypeTok{"orcid"}\FunctionTok{:} \StringTok{"0000{-}0000{-}0000{-}0001"}\FunctionTok{,}
      \DataTypeTok{"affiliations"}\FunctionTok{:} \OtherTok{[}
        \StringTok{"Affiliation 1"}\OtherTok{,}
        \StringTok{"Affiliation 2"}
      \OtherTok{]}\FunctionTok{,}
      \DataTypeTok{"status"}\FunctionTok{:} \OtherTok{[}\StringTok{"corresponding"}\OtherTok{,} \StringTok{"equal"}\OtherTok{]}
    \FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

The \texttt{email} field is recommended for all authors. The
\texttt{status} field is only useful for the corresponding author, and
to denote equal contributions. These informations are rendered on the
initial page. If an \texttt{orcid} is given, it will be linked on the
HTML and PDF versions.

Note that there is \emph{no need} to number the affiliations - a small
python script will take care of this automatically.

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

This template supports three types of abstracts, indicated in the
metadata file as \texttt{abstract}:

A regular \texttt{abstract} is defined as

\begin{Shaded}
\begin{Highlighting}[]
\ErrorTok{"abstract":} \ErrorTok{"A} \ErrorTok{very} \ErrorTok{long} \ErrorTok{string"}
\end{Highlighting}
\end{Shaded}

An itemized abstract is an array of strings, each representing a bullet
point:

\begin{Shaded}
\begin{Highlighting}[]
\ErrorTok{"abstract":} \OtherTok{[}
    \StringTok{"Point 1"}\OtherTok{,}
    \StringTok{"Point 2"}
\OtherTok{]}
\end{Highlighting}
\end{Shaded}

A structured abstract is an object with key-value pairs :

\begin{Shaded}
\begin{Highlighting}[]
\ErrorTok{"abstract":} \FunctionTok{\{}
    \DataTypeTok{"Location"}\FunctionTok{:} \StringTok{"Worldwide"}\FunctionTok{,}
    \DataTypeTok{"Organisms"}\FunctionTok{:} \StringTok{"Mammals"}
\FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{citation-style}{%
\subsection{Citation style}\label{citation-style}}

The \texttt{citationstyle} key corresponds to the name, with
\texttt{.csl} ommited, of a CSL stylesheet stored in the
\href{https://github.com/citation-style-language/}{citation style
language} repository. Note that there is no difference between main and
dependent styles, the build engine will take the correct steps to get
the correct style. The default is
\texttt{"citationstyle":\ "ecology-letters"}. There is a longer section
about references management later on.

\hypertarget{references-management}{%
\section{References management}\label{references-management}}

The references are managed by \texttt{pandoc}. Note that we \emph{do
not} use \texttt{pandoc-citeproc}, which was an external module for
older \texttt{pandoc} versions. References \emph{must} be stored in a
\texttt{references.bib} file, and that it would make sense to order it
alphabetically by key.

We use \href{https://www.zotero.org/}{Zotero} for references management,
and for the lab's manuscripts, we work from folders in a shared library
(with a folder for every manuscript).

It is recommedned to use the
\href{https://retorque.re/zotero-better-bibtex/}{Better BibTeX} plugin
for citation key generations, and auto-export of the shared library to
the \texttt{references.bib} file. We use a citation key format meant to
convey information on the author (first author full name), date (complet
year), and title (first three letters of the first two non-stop words).
It must be set in the Better BibTeX preferences as (you might need to
remove the line changes):

\begin{verbatim}
[auth:fold]
[year]
[title:fold:nopunctordash:skipwords:lower:select=1,1:substring=1,3:capitalize]
[title:fold:nopunctordash:skipwords:lower:select=2,2:substring=1,3:capitalize]
\end{verbatim}

It is a good idea to configure Better BibTeX to auto-export on change,
and to remove a lot of fields that are not strictly speaking required
for references. The list of fields we usually ignore is:

\begin{verbatim}
abstract,copyright,annotation,file,pmid,month,shorttitle,keywords
\end{verbatim}

The citations are done using the normal markdown syntax, where
\texttt{@Elton1927AniEco} produces Elton (1927), and
\texttt{{[}@Camerano1880EquViv{]}} produces (Camerano 1880).

\hypertarget{figures-tables-and-other-floats}{%
\section{Figures, Tables, and other
floats}\label{figures-tables-and-other-floats}}

Note that you can wrap the text of legends for both figures and tables.
This avoids the issue of having very long lines.

\hypertarget{mathematics}{%
\subsection{Mathematics}\label{mathematics}}

The following equation

\begin{equation}\protect\hypertarget{eq:eq1}{}{J'(p) = \frac{1}{\text{log}(S)}\times\left(-\sum p \times \text{log}(p)\right)}\label{eq:eq1}\end{equation}

is produced using

\begin{Shaded}
\begin{Highlighting}[]
\SpecialStringTok{$$J\textquotesingle{}(p) = }\SpecialCharTok{\textbackslash{}frac}\SpecialStringTok{\{1\}\{}\SpecialCharTok{\textbackslash{}text}\NormalTok{\{log\}}\SpecialStringTok{(S)\}}\SpecialCharTok{\textbackslash{}times}\SpecialStringTok{ ... $$}\NormalTok{ \{\#eq:eq1\}}
\end{Highlighting}
\end{Shaded}

and can be referenced using \texttt{@eq:eq1}, which will result in
eq.~\ref{eq:eq1}. Note that because we use \texttt{pandoc-crossref}, the
label ``eq.'' will be generated automatically.

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

Table legends go on the line after the table itself. To generate a
reference to the table, use \texttt{\{\#tbl:id\}} -- then, in the text,
you can use \texttt{\{@tbl:id\}} to refer to the table. For example, the
table below is tbl.~\ref{tbl:id}. You can remove the \emph{table} in
front by using \texttt{!@tbl:id}, or force it to be capitalized with
\texttt{\textbackslash{}*tbl:id}.

\hypertarget{tbl:id}{}
\begin{longtable}[]{@{}rrrrl@{}}
\caption{\label{tbl:id}This is a table, and its identifier is
\texttt{id} -- we can refer to it using \texttt{\{@tbl:id\}}. Note that
even if the table legend is written below the table itself, it will
appear on top in the PDF document.}\tabularnewline
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
Species\tabularnewline
\midrule
\endfirsthead
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
Species\tabularnewline
\midrule
\endhead
5.1 & 3.5 & 1.4 & 0.2 & setosa\tabularnewline
5.0 & 3.6 & 1.4 & 0.2 & setosa\tabularnewline
5.4 & 3.9 & 1.7 & 0.4 & setosa\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{figures}{%
\section{Figures}\label{figures}}

Figures can have a legend -- all figures \emph{must} be in the
\texttt{figures/} folder of the project, as it is also used for the
website. We recommend to use good resolution images, rather than PDFs,
or at least to have multiple versions available.

\begin{verbatim}
![This is the legend of the figure...](figures/figure.png){#fig:figure}
\end{verbatim}

\begin{figure}
\hypertarget{fig:figure}{%
\centering
\includegraphics{figures/figure.png}
\caption{This is the legend of the figure, which will be shown in the
margin in preprint mode, and underneath the figure in draft mode. The
legend can contain references, etc. It is advised to use a resolution of
at least 600dpi for the figures.}\label{fig:figure}
}
\end{figure}

We can now use \texttt{@fig:figure} to refer to fig.~\ref{fig:figure}.

\hypertarget{example-text}{%
\section{Example text}\label{example-text}}

Connectance, defined as the ratio of realized interactions on the total
number of potential interactions, is one of the most common descriptor
of network structure. In a bipartite network with \(T\) species at the
top, and \(B\) at the bottom, having a total of \(L\) interactions, it
is defined as \(Co = L/(T\times B)\). Connectance has a lower bound, as
the network cannot have fewer interactions that the number of species in
its more speciose level -- the minimal connectance is therefore
\(c_m = \text{max}(T,B)\). This makes the connectance of networks of
different sizes difficult to compare, especially since bipartite
networks tends to have a low connectance. For this reason, we used a
corrected version of connectance, defined as

\begin{equation}\protect\hypertarget{eq:cstar}{}{Co^\star=\frac{L-c_m}{T\times B-c_m} \,.}\label{eq:cstar}\end{equation}

\hypertarget{this-is-a-subsection}{%
\subsection{This is a subsection}\label{this-is-a-subsection}}

This takes values between 0 (the network has the minimal number of
interactions) and 1 (all species are connected), but is robust to
variations in species richness.

\hypertarget{this-is-another-subsection}{%
\subsection{This is another
subsection}\label{this-is-another-subsection}}

This takes values between 0 (the network has the minimal number of
interactions) and 1 (all species are connected), but is robust to
variations in species richness.

\hypertarget{some-non-standard-maths}{%
\subsection{Some non-standard maths}\label{some-non-standard-maths}}

The phylogenetic reconstruction of \(\hat{\mathscr{L}}\) and
\(\hat{\mathscr{R}}\) has an associated uncertainty, represented by the
breadth of the uniform distribution associated to each of their entries.
Therefore, we can use this information to assemble a
\emph{probabilistic} metaweb in the sense of
(\textbf{Poisot2016StrPro?}), \emph{i.e.} in which every interaction is
represented as a single, independent, Bernoulli event of probability
\(p\).

Specifically, we have adopted the following approach. For every entry in
\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\), we draw a value from
its distribution. This results in one instance of the possible left
(\(\hat{\mathscr{l}}\)) and right (\(\hat{\mathscr{r}}\)) subspaces for
the Canadian metaweb. These can be multiplied, to produce one matrix of
real values. Because the entries in \(\hat{\mathscr{l}}\) and
\(\hat{\mathscr{r}}\) are in the same space where \(\mathscr{L}\) and
\(\mathscr{R}\) were originally predicted, it follows that the threshold
\(\rho\) estimated for the European metaweb also applies. We use this
information to produce one random Canadian metaweb,
\(N = \hat{\mathscr{L}}\)\(\hat{\mathscr{R}}' \ge \rho\).

Because the intervals around some trait values can be broad (in fact,
probably broader than what they would actually be, see \emph{e.g.}
\textbf{Garland1999IntPhy?}), we repeat the above process
\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
where the probability of an interaction (here conveying our degree of
trust that it exists given the inferred trait distributions) is given by
the number of times where it appears across all random draws \(N\),
divided by the number of samples. An interaction with \(P_{i,j} = 1\)
means that these two species were predicted to interact in all
\(2\times 10^5\) random draws, etc..

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Camerano1880EquViv}{}%
Camerano, L. (1880). Dell'equilibrio dei viventi merce la reciproca
distruzione. \emph{Atti Della R. Accad. Delle Sci. Torino}, 15,
393--414.

\leavevmode\hypertarget{ref-Elton1927AniEco}{}%
Elton, C.S. (1927). \emph{Animal ecology}. University of Chicago Press.

\end{CSLReferences}

\end{document}

### 2021-09-11 preprint.tex
Deploy to GitHub Pages

--- 2021-09-11 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
 
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\geometry{includemp,
+            letterpaper,
+            top=1.0in,
+            bottom=2.510cm,
+            inner=0.5in,
+            outer=0.4in,
+            marginparwidth=1.9in,
+            marginparsep=0.3in}
+
+\usepackage[singlelinecheck=off]{caption}
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+\usepackage{floatrow}
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+\floatsetup[table]{margins=hangoutside,
+             facing=yes,
+             capposition=beside,
+             capbesideposition={center,outside},
+             floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
+\setcounter{secnumdepth}{5}
 
-\doublespacing
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
-\vskip 5em
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
 
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
+manuscripts using markdown and github actions}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{1,2,‡}, %
 Peregrin\,Took%
 %
-\,\textsuperscript{3,4}\quad %
+\,\textsuperscript{3,4}, %
 Merriadoc\,Brandybuck%
@@
 \,\textsuperscript{5,4,‡}
-
-\textsuperscript{1}\,Université de
-Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
-Sciences\quad \textsuperscript{3}\,Inn of the Prancing
-Pony\quad \textsuperscript{4}\,Fellowship of the
-Ring\quad \textsuperscript{5}\,Green Dragon Inn
-
+\vskip 1em
+\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
+Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
+Prancing Pony; \textsuperscript{4}\,Fellowship of the
+Ring; \textsuperscript{5}\,Green Dragon Inn\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\
-
+\vskip 1em
 \textbf{Correspondance to:}\\
 Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
+}
+\end{flushleft}
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
 
-\clearpage
-\thispagestyle{empty}
-
-\vfill
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+pandoc\\pandoc-crossref\\github actions\\}
+}
 
@@
 
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2021-09-11 draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@dbd6d6d0b52cba29b1d553dd908648a4fce9788d 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@e25b19d09dae84024cc8c6ee0a19767b0fe31960 🚀

@@
 
+The process of deploying this template has been \emph{greatly}
+streamlined from previous versions:
+
 \begin{itemize}
@@
 \item
-  Edit this README!
+  Edit \texttt{README.md} with your own text, commit, and push
 \item
-  Add an \texttt{ACCESS\_TOKEN} secret to your repository
-\item
-  Trigger a build by pushing a commit - the builds are only active on
-  the \texttt{main} (\textbf{not} \texttt{master}) branch, and on pull
+  This push will trigger the first build - the builds are only active on
+  the \texttt{main} branch (\emph{not} \texttt{master}!), and on pull
   requests
@@
   Go to \texttt{http://you.github.io/repo-name/} to view the html
-  version and the PDFs
+  version, and get access to the PDFs
 \item
@@
   authors
-\item
-  Edit the \texttt{manuscript.md} file to make changes to your text
 \end{itemize}
+
+In particular, note that \emph{you do not need} to create a personnal
+access token to deploy to \texttt{gh-pages} (from where the website is
+served).
 

### 2021-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@2b7a496ba0284efd37d0007167d17b9454d95631 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@31363ca119e8c6a3d54b557e6f16021940d3167d 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@20824b61006c91535f1d922d11fd9c9f00437fb3 🚀

@@
 \documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
             outer=0.4in,
-            marginparwidth=1.9in,
+            marginparwidth=2.1in,
             marginparsep=0.3in}
@@
 
-The first three fields are the title, language, and license. It's
-probably advisable not to change these, and there are chances that the
-logo on the PDF will not capture the values made here (this will have to
-be, maybe, fixed at some point).
+The title is a field in the \texttt{metadata.json}:
 
@@
 \FunctionTok{\{}
-    \DataTypeTok{"title"}\FunctionTok{:} \StringTok{"Preprint template"}\FunctionTok{,}
-    \DataTypeTok{"license"}\FunctionTok{:} \StringTok{"CC{-}BY"}\FunctionTok{,}
-    \DataTypeTok{"language"}\FunctionTok{:} \StringTok{"en"}
+    \DataTypeTok{"title"}\FunctionTok{:} \StringTok{"Preprint template"}
 \FunctionTok{\}}

### 2021-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@10d3ec7b9a0f1971639bbb23d35465392c675424 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@5062ccb647f4ebdddcbda9a464ecccad739503d5 🚀

@@
             bottom=2.510cm,
-            inner=0.5in,
-            outer=0.4in,
-            marginparwidth=2.1in,
-            marginparsep=0.3in}
+            left=0.35in,
+            right=0.35in,
+            marginparwidth=2.0in,
+            marginparsep=0.35in}
 
@@
               floatwidth=\textwidth}
-\floatsetup[table]{margins=hangoutside,
-             facing=yes,
+\floatsetup[table]{margins=hangright,
+             facing=no,
              capposition=beside,

### 2021-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@8d51cc2b20940e8fef109e7a46befa7c19c71f4a 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@f8a80127fd198dec6d1cd3171e9af8a62b142f0e 🚀

@@
             letterpaper,
-            top=1.0in,
-            bottom=2.510cm,
-            left=0.35in,
-            right=0.35in,
-            marginparwidth=2.0in,
-            marginparsep=0.35in}
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
 
 \usepackage[singlelinecheck=off]{caption}
+
 \captionsetup{
@@
 }
+
 \usepackage{floatrow}
+
 \floatsetup[figure]{margins=hangright,
@@
               floatwidth=\textwidth}
-\floatsetup[table]{margins=hangright,
-             facing=no,
-             capposition=beside,
-             capbesideposition={center,outside},
-             floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 

### 2022-09-11 .assets/scripts/abstract.jl
🛑 porting to jl

@@ -1,0 +1,28 @@
+import JSON
+
+# Read the metadata
+metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
+
+# Dispatch on abstract type
+function format_abstract(abstract::Dict{String, Any})
+    data = Dict{String,Any}(["structured" => true])
+    data["content"] = [Dict(["key" => key, "value" => value]) for (key,value) in abstract]
+    return data
+end
+
+function format_abstract(abstract::String)
+    data = Dict{String, Any}(["regular" => true])
+    data["content"] = abstract
+    return data
+end
+
+function format_abstract(abstract::Vector{T}) where {T}
+    data = Dict{String, Any}(["itemized" => true])
+    data["content"] = [element for element in abstract]
+    return data
+end
+
+# Write the file
+open("abstract.json", "w") do json_file
+    JSON.print(json_file, format_abstract(metadata["abstract"]), 4)
+end

### 2022-09-11 .assets/scripts/abstract.py

@@ -1,24 +1,0 @@
-import json
-
-with open("metadata.json") as mdfile:
-    metadata = json.load(mdfile)
-
-abstract = {}
-abstract["abstractdata"] = {}
-
-if type(metadata["abstract"]) == dict:
-    abstract["abstractdata"]["structured"] = True
-    abstract["abstractdata"]["content"] = [{"key": header, "value": metadata["abstract"][header]} for header in metadata["abstract"]]
-
-if type(metadata["abstract"]) == list:
-    abstract["abstractdata"]["itemized"] = True
-    abstract["abstractdata"]["content"] = [header for header in metadata["abstract"]]
-
-if type(metadata["abstract"]) == str:
-    abstract["abstractdata"]["regular"] = True
-    abstract["abstractdata"]["content"] = metadata["abstract"]
-
-with open("abstract.json", "w") as outfile:
-    json.dump(abstract, outfile, sort_keys=False,
-              indent=4, separators=(',', ': '))
-    outfile.write('\n')

### 2022-09-11 .assets/scripts/affiliations.jl

@@ -1,0 +1,32 @@
+import JSON
+
+# Read the metadata
+metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
+
+authors = metadata["authors"]
+affiliation_to_number = Dict{String, Integer}()
+
+for author in authors
+    affiliations = author["affiliations"]
+    for affiliation in affiliations
+        if ~haskey(affiliation_to_number, affiliation)
+            affiliation_to_number[affiliation] = length(affiliation_to_number) + 1
+        end
+    end
+end
+
+for author in authors
+    author["affilcode"] =
+        sort([affiliation_to_number[affiliation] for affiliation in author["affiliations"]])
+    delete!(author, "affiliations")
+end
+
+affiliations = Dict{String, Any}()
+affiliations["authors"] = authors
+affiliations["institutions"] = []
+while ~isempty(affiliation_to_number)
+    id, idx = findmin(collect(values(affiliation_to_number)))
+    name = collect(keys(affiliation_to_number))[idx]
+    delete!(affiliation_to_number, name)
+    push!(affiliations["institutions"], Dict(["id" => id, "name" => name]))
+end

### 2022-09-11 .assets/scripts/affiliations.py

@@ -1,7 +1,3 @@
-import subprocess
-import json
-import os
-
 with open("metadata.json") as jsfile:
     metadata = json.load(jsfile)
 
@@ -17,26 +13,6 @@ for author in authors:
     for affiliation in affiliations:
         if not (affiliation in affiliation_to_number.keys()):
             affiliation_to_number[affiliation] = len(affiliation_to_number) + 1
-    # BIORXIV info block
-    if "email" in author.keys():
-        biorxiv.write(author["email"])
-    biorxiv.write("\t")
-    # Institution
-    biorxiv.write(affiliations[0])
-    biorxiv.write("\t")
-    # Name
-    biorxiv.write(author["givennames"])
-    biorxiv.write("\t")
-    biorxiv.write("\t")
-    biorxiv.write(author["familyname"])
-    biorxiv.write("\t")
-    biorxiv.write("\t")
-    biorxiv.write("\t")
-    biorxiv.write("\t")
-    biorxiv.write("\t")
-    if "orcid" in author.keys():
-        biorxiv.write(author["orcid"])
-    biorxiv.write("\n")
     
 biorxiv.close()
 

### 2022-09-11 .assets/scripts/bibliography.jl

@@ -1,0 +1,28 @@
+import JSON
+
+metadata = JSON.parsefile(joinpath(pwd(), "references.json"))
+
+fields_to_drop = [
+    "source",
+    "abstract",
+    "language",
+    "accessed",
+    "container-title-short",
+    "title-short",
+    "ISSN",
+    "call-number",
+    "number-of-pages",
+    "ISBN",
+    "note",
+    "annote",
+]
+
+for reference in references
+    for field in fields_to_drop
+        delete!(reference, field)
+    end
+end
+
+open("references.json", "w") do json_file
+    return JSON.print(json_file, references, 4)
+end

### 2022-09-11 .assets/scripts/bibliography.py

@@ -1,18 +1,0 @@
-import subprocess
-import json
-import os
-
-with open("references.json") as jsfile:
-    references = json.load(jsfile)
-
-# Fields to remove
-fields = ["source", "abstract", "language", "accessed", "container-title-short",
-          "title-short", "ISSN", "call-number", "number-of-pages", "ISBN", "note", "annote"]
-for reference in references:
-    for field in fields:
-        reference.pop(field, None)
-
-with open("references.json", "w") as outfile:
-    json.dump(references, outfile, sort_keys=True,
-              indent=4, separators=(',', ': '))
-    outfile.write('\n')

### 2022-09-11 .assets/scripts/citationstyle.jl

@@ -1,0 +1,14 @@
+import Downloads
+import JSON
+
+metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
+
+local_file = joinpath(pwd(), ".assets", "citationstyle.csl")
+
+try
+    remote_url = "https://raw.githubusercontent.com/citation-style-language/styles/master/$(metadata["citationstyle"]).csl"
+    Downloads.download(remote_url, local_file)
+catch err
+    remote_url = "https://raw.githubusercontent.com/citation-style-language/styles/master/dependent/$(metadata["citationstyle"]).csl"
+    Downloads.download(remote_url, local_file)
+end

### 2022-09-11 .assets/scripts/citationstyle.py

@@ -1,17 +1,0 @@
-import json
-
-with open("metadata.json") as mdfile:
-    metadata = json.load(mdfile)
-
-# 
-
-from urllib import request
-
-local_file = '.assets/citationstyle.csl'
-
-try:
-    remote_url = "https://raw.githubusercontent.com/citation-style-language/styles/master/%s.csl" % metadata["citationstyle"]
-    request.urlretrieve(remote_url, local_file)
-except request.HTTPError:
-    remote_url = "https://raw.githubusercontent.com/citation-style-language/styles/master/dependent/%s.csl" % metadata["citationstyle"]
-    request.urlretrieve(remote_url, local_file)

### 2022-09-11 .assets/scripts/affiliations.jl
⚙️ update all format scripts to julia

@@ -17,7 +17,11 @@ end
 
 for author in authors
     author["affilcode"] =
-        sort([affiliation_to_number[affiliation] for affiliation in author["affiliations"]])
+        sort(
+            Any[
+                affiliation_to_number[affiliation] for affiliation in author["affiliations"]
+            ],
+        )
     delete!(author, "affiliations")
 end
 
@@ -29,4 +33,35 @@ while ~isempty(affiliation_to_number)
     name = collect(keys(affiliation_to_number))[idx]
     delete!(affiliation_to_number, name)
     push!(affiliations["institutions"], Dict(["id" => id, "name" => name]))
+end
+
+affiliations["metadata"] = Dict()
+affiliations["metadata"]["corresponding"] = []
+
+add_equal_sign = true
+for author in affiliations["authors"]
+    if haskey(author, "status")
+        if "equal" in author["status"]
+            push!(author["affilcode"], "‡")
+            if add_equal_sign
+                affiliations["metadata"]["equalcontributions"] =
+                    Dict(["id" => "‡", "name" => "Equal contributions"])
+                add_equal_sign = false
+            end
+        end
+        if "corresponding" in author["status"]
+            push!(affiliations["metadata"]["corresponding"],
+                Dict([
+                    "given" => author["givennames"],
+                    "family" => author["familyname"],
+                    "email" => author["email"],
+                ]),
+            )
+        end
+    end
+end
+
+# Write the file
+open("affiliations.json", "w") do json_file
+    return JSON.print(json_file, affiliations, 4)
 end

### 2022-09-11 .assets/scripts/affiliations.py

@@ -1,47 +1,0 @@
-with open("metadata.json") as jsfile:
-    metadata = json.load(jsfile)
-
-biorxiv = open("author_template.tsv", "w")
-biorxiv.write("Email	Institution	First Name	Middle Name(s)/Initial(s)	Last Name	Suffix	Corresponding Author	Home Page URL	Collaborative Group/Consortium	ORCiD\n")
-
-# Fields to remove
-authors = metadata["authors"]
-affiliation_to_number = {}
-
-for author in authors:
-    affiliations = author["affiliations"]
-    for affiliation in affiliations:
-        if not (affiliation in affiliation_to_number.keys()):
-            affiliation_to_number[affiliation] = len(affiliation_to_number) + 1
-    
-biorxiv.close()
-
-for author in authors:
-    author["affilcode"] = [affiliation_to_number[affiliation]
-                            for affiliation in author["affiliations"]]
-    author.pop("affiliations", None)
-
-affiliations = {}
-affiliations["authors"] = authors
-affiliations["institutions"] = [{"id": v, "name": k} for k, v in sorted(
-    affiliation_to_number.items(), key=lambda item: item[1])]
-
-affiliations["metadata"] = {}
-affiliations["metadata"]["corresponding"] = []
-
-# Check authorship and correspondance
-toadd = True
-for author in affiliations["authors"]:
-    if "status" in author.keys():
-        if "equal" in author["status"]:
-            author["affilcode"].append("‡")
-            if toadd:
-                affiliations["metadata"]["equalcontributions"] = {"id": "‡", "name": "These authors contributed equally to the work"}
-                toadd = False
-        if "corresponding" in author["status"]:
-            affiliations["metadata"]["corresponding"].append({"given": author["givennames"], "family": author["familyname"], "email": author["email"]})
-
-with open("affiliations.json", "w") as outfile:
-    json.dump(affiliations, outfile, sort_keys=False,
-              indent=4, separators=(',', ': '))
-    outfile.write('\n')

### 2022-09-11 .assets/scripts/bibliography.jl
🐛 reference field

@@ -1,6 +1,6 @@
 import JSON
 
-metadata = JSON.parsefile(joinpath(pwd(), "references.json"))
+references = JSON.parsefile(joinpath(pwd(), "references.json"))
 
 fields_to_drop = [
     "source",

### 2022-09-11 .assets/scripts/abstract.jl
🧹 format

@@ -5,8 +5,8 @@ metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
 
 # Dispatch on abstract type
 function format_abstract(abstract::Dict{String, Any})
-    data = Dict{String,Any}(["structured" => true])
-    data["content"] = [Dict(["key" => key, "value" => value]) for (key,value) in abstract]
+    data = Dict{String, Any}(["structured" => true])
+    data["content"] = [Dict(["key" => key, "value" => value]) for (key, value) in abstract]
     return data
 end
 
@@ -24,5 +24,5 @@ end
 
 # Write the file
 open("abstract.json", "w") do json_file
-    JSON.print(json_file, format_abstract(metadata["abstract"]), 4)
+    return JSON.print(json_file, format_abstract(metadata["abstract"]), 4)
 end

### 2022-09-12 .assets/scripts/affiliations.jl
🐛 fix variable scope

@@ -46,7 +46,7 @@ for author in affiliations["authors"]
             if add_equal_sign
                 affiliations["metadata"]["equalcontributions"] =
                     Dict(["id" => "‡", "name" => "Equal contributions"])
-                add_equal_sign = false
+                global add_equal_sign = false
             end
         end
         if "corresponding" in author["status"]

### 2022-09-12 draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@31363ca119e8c6a3d54b557e6f16021940d3167d 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@895bf2fb607db28eae3d30e77d03a48206b7f6ce 🚀

@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{,,}\quad %
 Peregrin\,Took%
 %
-\,\textsuperscript{3,4}\quad %
+\,\textsuperscript{,}\quad %
 Merriadoc\,Brandybuck%
 %
-\,\textsuperscript{5,4,‡}
+\,\textsuperscript{,,}
 
@@
 
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+\textsuperscript{‡}\,Equal contributions\\
 
@@
 \vfill
-
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
 
@@
 appear on top in the PDF document.}\tabularnewline
-\toprule
-Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
-Species\tabularnewline
-\midrule
+\toprule()
+Sepal.Length & Sepal.Width & Petal.Length & Petal.Width & Species \\
+\midrule()
 \endfirsthead
-\toprule
-Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
-Species\tabularnewline
-\midrule
+\toprule()
+Sepal.Length & Sepal.Width & Petal.Length & Petal.Width & Species \\
+\midrule()
 \endhead
-5.1 & 3.5 & 1.4 & 0.2 & setosa\tabularnewline
-5.0 & 3.6 & 1.4 & 0.2 & setosa\tabularnewline
-5.4 & 3.9 & 1.7 & 0.4 & setosa\tabularnewline
-\bottomrule
+5.1 & 3.5 & 1.4 & 0.2 & setosa \\
+5.0 & 3.6 & 1.4 & 0.2 & setosa \\
+5.4 & 3.9 & 1.7 & 0.4 & setosa \\
+\bottomrule()
 \end{longtable}
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Camerano1880EquViv}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Camerano1880EquViv}{}}%
 Camerano, L. (1880). Dell'equilibrio dei viventi merce la reciproca
@@
 
-\leavevmode\hypertarget{ref-Elton1927AniEco}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Elton1927AniEco}{}}%
 Elton, C.S. (1927). \emph{Animal ecology}. University of Chicago Press.

### 2022-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@895bf2fb607db28eae3d30e77d03a48206b7f6ce 🚀

@@
 %
-\,\textsuperscript{1,2,‡}, %
+\,\textsuperscript{,,}, %
 Peregrin\,Took%
 %
-\,\textsuperscript{3,4}, %
+\,\textsuperscript{,}, %
 Merriadoc\,Brandybuck%
 %
-\,\textsuperscript{5,4,‡}
+\,\textsuperscript{,,}
 \vskip 1em
@@
 Ring; \textsuperscript{5}\,Green Dragon Inn\\
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+\textsuperscript{‡}\,Equal contributions\\
 \vskip 1em
@@
 }
-
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
 

### 2022-09-12 .assets/scripts/affiliations.jl
🐛 output affil

@@ -18,8 +18,8 @@ end
 for author in authors
     author["affilcode"] =
         sort(
-            Any[
-                affiliation_to_number[affiliation] for affiliation in author["affiliations"]
+            String[
+                "$(affiliation_to_number[affiliation])" for affiliation in author["affiliations"]
             ],
         )
     delete!(author, "affiliations")

### 2022-09-12 .assets/scripts/affiliations.jl
🐛 affil id

@@ -4,13 +4,13 @@ import JSON
 metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
 
 authors = metadata["authors"]
-affiliation_to_number = Dict{String, Integer}()
+affiliation_to_number = Dict{String, String}()
 
 for author in authors
     affiliations = author["affiliations"]
     for affiliation in affiliations
         if ~haskey(affiliation_to_number, affiliation)
-            affiliation_to_number[affiliation] = length(affiliation_to_number) + 1
+            affiliation_to_number[affiliation] = "$(length(affiliation_to_number) + 1)"
         end
     end
 end

### 2022-09-12 draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@e2d1f3d8de8f52c9d1227cf237fc2a0b94f8ba4a 🚀

@@
 
-This template uses \texttt{pandoc} (and a few additional python glue
-scripts) to facilitate the production of scientific articles using a
-standard markdown file. The objective is to ensure that standard
+This template uses \texttt{pandoc} (and a few additional \emph{Julia}
+glue scripts) to facilitate the production of scientific articles using
+a standard markdown file. The objective is to ensure that standard
 markdown (with the important exception of the \texttt{pandoc-crossref}
@@
 platform), a ``draft'' style PDF (double-spaced, numbered lines, figures
-at the end), and a ``preprint'' style PDF (with slightly more
-reader-friendly pagination).
+at the end), and a ``preprint'' style PDF (with more reader-friendly
+pagination).
 

### 2022-09-12 .assets/scripts/manuscript-name.jl
✨ filename

@@ -1,0 +1,34 @@
+import JSON
+import Languages
+import Dates
+
+metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
+
+title = lowercase(metadata["title"])
+title_tokens = setdiff(split(title, " "), Languages.stopwords(Languages.English()))
+title_placeholder = join(title_tokens[1:min(2, length(title_tokens))], "_")
+
+ms_year = Dates.year(Dates.today())
+
+author_string = ""
+
+if length(metadata["authors"]) == 1
+    global author_string = only(metadata["authors"])["familyname"]
+elseif length(metadata["authors"]) == 2
+    global author_string =
+        metadata["authors"][1]["familyname"] * "_and_" *
+        metadata["authors"][1]["familyname"]
+else
+    global author_string =
+        metadata["authors"][1]["familyname"] * "_et_al"
+end
+
+filename = join([author_string, ms_year, title_placeholder], "_")
+
+open("filename", "w") do f
+    return write(f, filename)
+end
+
+open("filename.json", "w") do f
+    return JSON.print(f, Dict(["filename" => filename]), 4)
+end

### 2022-09-12 .assets/scripts/metadata.jl
✨ collapse all metadata to new file

@@ -1,0 +1,21 @@
+import JSON
+
+metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
+
+delete!(metadata, "abstract")
+abstract = JSON.parsefile(joinpath(pwd(), "abstract.json"))
+metadata["abstract"] = abstract
+
+delete!(metadata, "authors")
+affiliations = JSON.parsefile(joinpath(pwd(), "affiliations.json"))
+metadata["authors"] = affiliations["authors"]
+metadata["authorship"] = affiliations["metadata"]
+metadata["institutions"] = affiliations["institutions"]
+
+metadata["filename"] = JSON.parsefile(joinpath(pwd(), "filename.json"))["filename"]
+
+# Write the file
+open("manuscript-metadata.json", "w") do json_file
+    return JSON.print(json_file, metadata, 4)
+end
+

### 2022-09-12 .assets/scripts/affiliations.jl
rename

@@ -16,7 +16,7 @@ for author in authors
 end
 
 for author in authors
-    author["affilcode"] =
+    author["affiliation"] =
         sort(
             String[
                 "$(affiliation_to_number[affiliation])" for affiliation in author["affiliations"]
@@ -42,7 +42,7 @@ add_equal_sign = true
 for author in affiliations["authors"]
     if haskey(author, "status")
         if "equal" in author["status"]
-            push!(author["affilcode"], "‡")
+            push!(author["affiliation"], "‡")
             if add_equal_sign
                 affiliations["metadata"]["equalcontributions"] =
                     Dict(["id" => "‡", "name" => "Equal contributions"])

### 2022-09-12 .assets/scripts/affiliations.jl
fig abstract and equal authorship

@@ -44,7 +44,7 @@ for author in affiliations["authors"]
         if "equal" in author["status"]
             push!(author["affiliation"], "‡")
             if add_equal_sign
-                affiliations["metadata"]["equalcontributions"] =
+                affiliations["metadata"]["equal"] =
                     Dict(["id" => "‡", "name" => "Equal contributions"])
                 global add_equal_sign = false
             end

### 2022-12-20 .assets/scripts/metadata.jl
🧹 metadata

@@ -18,4 +18,3 @@ metadata["filename"] = JSON.parsefile(joinpath(pwd(), "filename.json"))["filenam
 open("manuscript-metadata.json", "w") do json_file
     return JSON.print(json_file, metadata, 4)
 end
-

### 2022-12-20 Poisot_et_al_2022_template_prepare_draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@d9efd7a20f41f449634667aa7f2f7139a6d3c76a 🚀

--- 2022-09-12 draft.tex
@@
 \setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
  {% don't indent paragraphs
@@
 %
-\,\textsuperscript{,,}\quad %
+\,\textsuperscript{1,2,‡}\quad %
 Peregrin\,Took%
 %
-\,\textsuperscript{,}\quad %
+\,\textsuperscript{3,4}\quad %
 Merriadoc\,Brandybuck%
 %
-\,\textsuperscript{,,}
+\,\textsuperscript{4,5,‡}
 
@@
 
-\textsuperscript{‡}\,Equal contributions\\
+\textbf{Correspondance to:}\\
 
-\textbf{Correspondance to:}\\
-Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
+\vfill
+
+        {\bfseries Purpose:}\,This template provides a series of scripts
+to render a markdown document into an interactive website and a series
+of PDFs.\\%
+        {\bfseries Internals:}\,GitHub actions and a series of python
+scritpts. The markdown is handled with \texttt{pandoc}.\\%
+        {\bfseries Motivation:}\,It makes collaborating on text with
+GitHub easier, and means that we never need to think about the
+output.\\%
 

### 2022-12-20 Poisot_et_al_2022_template_prepare_preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@d9efd7a20f41f449634667aa7f2f7139a6d3c76a 🚀

--- 2022-09-12 preprint.tex
@@
 %
-\,\textsuperscript{,,}, %
+\,\textsuperscript{1,2,‡}, %
 Peregrin\,Took%
 %
-\,\textsuperscript{,}, %
+\,\textsuperscript{3,4}, %
 Merriadoc\,Brandybuck%
 %
-\,\textsuperscript{,,}
+\,\textsuperscript{4,5,‡}
 \vskip 1em
@@
 Ring; \textsuperscript{5}\,Green Dragon Inn\\
-\textsuperscript{‡}\,Equal contributions\\
 \vskip 1em
 \textbf{Correspondance to:}\\
-Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
 }
@@
 }
+
+        {\bfseries Purpose:}\,This template provides a series of scripts
+to render a markdown document into an interactive website and a series
+of PDFs.\\%
+        {\bfseries Internals:}\,GitHub actions and a series of python
+scritpts. The markdown is handled with \texttt{pandoc}.\\%
+        {\bfseries Motivation:}\,It makes collaborating on text with
+GitHub easier, and means that we never need to think about the
+output.\\%
 

### 2023-01-15 Poisot_et_al_2023_template_prepare_draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@a302d3933d5e797ee4af6e7e2a421e1c856a88a9 🚀

--- 2022-12-20 Poisot_et_al_2022_template_prepare_draft.tex
@@
 Because the intervals around some trait values can be broad (in fact,
-probably broader than what they would actually be, see \emph{e.g.}
-\textbf{Garland1999IntPhy?}), we repeat the above process
-\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
-where the probability of an interaction (here conveying our degree of
-trust that it exists given the inferred trait distributions) is given by
-the number of times where it appears across all random draws \(N\),
-divided by the number of samples. An interaction with \(P_{i,j} = 1\)
-means that these two species were predicted to interact in all
-\(2\times 10^5\) random draws, etc..
+probably broader than what they would actually be), we repeat the above
+process \(2\times 10^5\) times, which results in a probabilistic metaweb
+\(P\), where the probability of an interaction (here conveying our
+degree of trust that it exists given the inferred trait distributions)
+is given by the number of times where it appears across all random draws
+\(N\), divided by the number of samples. An interaction with
+\(P_{i,j} = 1\) means that these two species were predicted to interact
+in all \(2\times 10^5\) random draws, etc..
 

### 2023-01-15 .assets/scripts/filename.jl
✨ remove punctuation from title

@@ -1,10 +1,11 @@
 import JSON
 import Languages
 import Dates
+import Unicode
 
 metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
 
-title = lowercase(metadata["title"])
+title = filter(!Unicode.ispunct, lowercase(metadata["title"]))
 title_tokens = setdiff(split(title, " "), Languages.stopwords(Languages.English()))
 title_placeholder = join(title_tokens[1:min(2, length(title_tokens))], "_")
 

### 2023-01-17 .assets/scripts/filename.jl
fix authorship blocks

@@ -18,7 +18,7 @@ if length(metadata["authors"]) == 1
 elseif length(metadata["authors"]) == 2
     global author_string =
         metadata["authors"][1]["familyname"] * "_and_" *
-        metadata["authors"][1]["familyname"]
+        metadata["authors"][2]["familyname"]
 else
     global author_string =
         metadata["authors"][1]["familyname"] * "_et_al"

### 2023-01-24 Poisot_et_al_2023_template_prepare_draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@ff6a660bd329ca2c1099a5e8976df8c23074179b 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@2fa588414a595ad382e315343a735c4f6e80d7c7 🚀

@@
 \usepackage{lastpage}
+
+\usepackage{gensymb}
 
@@
 
+\textsuperscript{‡}\,Equal contributions\\
+
 \textbf{Correspondance to:}\\
+Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
 
@@
 \begin{verbatim}
-[auth:fold]
-[year]
-[title:fold:nopunctordash:skipwords:lower:select=1,1:substring=1,3:capitalize]
-[title:fold:nopunctordash:skipwords:lower:select=2,2:substring=1,3:capitalize]
+auth.fold.fold + year + title.fold.nopunctordash.skipwords.lower.select(1,1).capitalize()
 \end{verbatim}

### 2023-01-24 Poisot_et_al_2023_template_prepare_preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@ff6a660bd329ca2c1099a5e8976df8c23074179b 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@2fa588414a595ad382e315343a735c4f6e80d7c7 🚀

@@
 Ring; \textsuperscript{5}\,Green Dragon Inn\\
+\textsuperscript{‡}\,Equal contributions\\
 \vskip 1em
 \textbf{Correspondance to:}\\
+Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
 }

### 2023-02-14 .assets/scripts/appendix.sh
✨ appendix + script

@@ -1,0 +1,3 @@
+for file in appendix/*.md; do
+    pandoc "$file" -s -o dist/"${file%.md}".pdf --citeproc --bibliography=references.json --csl .assets/citationstyle.csl --metadata-file=manuscript-metadata.json --template=.assets/templates/appendix.tex
+done

### 2023-02-26 .assets/scripts/appendix.sh
attempt at building appendix

@@ -1,3 +1,3 @@
 for file in appendix/*.md; do
-    pandoc "$file" -s -o dist/"${file%.md}".pdf --citeproc --bibliography=references.json --csl .assets/citationstyle.csl --metadata-file=manuscript-metadata.json --template=.assets/templates/appendix.tex
+    pandoc "$file" -s -o dist/"appendix_${file%.md}".tex --citeproc --bibliography=references.json --csl .assets/citationstyle.csl --metadata-file=manuscript-metadata.json --template=.assets/templates/appendix.tex
 done

### 2023-02-26 .typesetter/scripts/abstract.jl
👊 new github action

@@ -1,28 +1,0 @@
-import JSON
-
-# Read the metadata
-metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
-
-# Dispatch on abstract type
-function format_abstract(abstract::Dict{String, Any})
-    data = Dict{String, Any}(["structured" => true])
-    data["content"] = [Dict(["key" => key, "value" => value]) for (key, value) in abstract]
-    return data
-end
-
-function format_abstract(abstract::String)
-    data = Dict{String, Any}(["regular" => true])
-    data["content"] = abstract
-    return data
-end
-
-function format_abstract(abstract::Vector{T}) where {T}
-    data = Dict{String, Any}(["itemized" => true])
-    data["content"] = [element for element in abstract]
-    return data
-end
-
-# Write the file
-open("abstract.json", "w") do json_file
-    return JSON.print(json_file, format_abstract(metadata["abstract"]), 4)
-end

### 2023-02-26 .typesetter/scripts/appendix.sh

@@ -1,3 +1,0 @@
-for file in appendix/*.md; do
-    pandoc "$file" -s -o dist/"appendix_${file%.md}".tex --citeproc --bibliography=references.json --csl .assets/citationstyle.csl --metadata-file=manuscript-metadata.json --template=.assets/templates/appendix.tex
-done

### 2023-02-26 .typesetter/scripts/citationstyle.jl

@@ -1,14 +1,0 @@
-import Downloads
-import JSON
-
-metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
-
-local_file = joinpath(pwd(), ".assets", "citationstyle.csl")
-
-try
-    remote_url = "https://raw.githubusercontent.com/citation-style-language/styles/master/$(metadata["citationstyle"]).csl"
-    Downloads.download(remote_url, local_file)
-catch err
-    remote_url = "https://raw.githubusercontent.com/citation-style-language/styles/master/dependent/$(metadata["citationstyle"]).csl"
-    Downloads.download(remote_url, local_file)
-end

### 2023-02-26 .typesetter/scripts/filename.jl

@@ -1,35 +1,0 @@
-import JSON
-import Languages
-import Dates
-import Unicode
-
-metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
-
-title = filter(!Unicode.ispunct, lowercase(metadata["title"]))
-title_tokens = setdiff(split(title, " "), Languages.stopwords(Languages.English()))
-title_placeholder = join(title_tokens[1:min(2, length(title_tokens))], "_")
-
-ms_year = Dates.year(Dates.today())
-
-author_string = ""
-
-if length(metadata["authors"]) == 1
-    global author_string = only(metadata["authors"])["familyname"]
-elseif length(metadata["authors"]) == 2
-    global author_string =
-        metadata["authors"][1]["familyname"] * "_and_" *
-        metadata["authors"][2]["familyname"]
-else
-    global author_string =
-        metadata["authors"][1]["familyname"] * "_et_al"
-end
-
-filename = join([author_string, ms_year, title_placeholder], "_")
-
-open("filename", "w") do f
-    return write(f, filename)
-end
-
-open("filename.json", "w") do f
-    return JSON.print(f, Dict(["filename" => filename]), 4)
-end

### 2023-02-27 .assets/scripts/filename.jl
Allow for author names with white spaces
Fixed `filename.jl` so that it can handle author family names with white spaces.

It does that by stripping all white spaces in the filename.

The fix solves an issues with pandoc, that would result in a `file not found error`.

@@ -25,6 +25,7 @@ else
 end
 
 filename = join([author_string, ms_year, title_placeholder], "_")
+filename = filter(x -> !isspace(x), filename)
 
 open("filename", "w") do f
     return write(f, filename)
